Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-02-26 TEBenchmarkPaper/article.tex
Minor fixes

This justifies a rewrite rule for splitting a single $\Map$ call into multiple
independent calls dealing with different sections of a list. Such rules are
useful optimisations since each call can be evaluated in parallel, leading to
the ``map/reduce'' programming paradigm.

@@

{\bf Comprehensibility} is the complexity of a statement. Simpler
statements are considered more interesting, and many of the search
algorithms explore simpler/smaller statements before complex/larger
ones, to more efficiently find those which are interesting.

@@

All four of these systems use testing to check for counterexamples, which
ensures results are empirically plausible and applicable (conditions are
satisfiable, types are inhabited, etc.). They also use a small-to-large search
order, ensuring more easily-comprehensibile conjectures are explored first.

IsaCoSy ensures novelty using a constraint system, such that no generated
expression can be simplified using a previously-found equation. The other
systems use post-hoc filters based on unification and rewriting rules
(derived via the Knuth-Bendix completion algorithm) to discard expressions or
equations which are special-cases of some other, more general result.

@@

Differences in background and motivation continue to be relevant
today. While the majority of work in automating mathematics has been
in symbolic manipulation and theorem proving, we are concerned here
with other aspects of mathematics, including the construction of conjectures,
(counter-)examples and theorems. These tasks, along with the formation of new
definitions and concepts, are varyingly known as
``Automated Theory Formation''~\cite{lenat:77,colton:book},
``Mathematical Theory Exploration''~\cite{buchberger:06} (also sometimes
prefaced with ``Computer-Aided'', ``Automated'' or ``Algorithm-Supported''),
``Automated Mathematical Discovery''~\cite{epstein:91,colton:interestingness,esarm2008},
``Concept Formation in Discovery Systems''~\cite{haase}, and
``Automated Theorem Discovery''~\cite{roy}. Such a plethora of terminology can
be unhelpful and can mask similarities between the different fields. In
particular, the twin strands of Automated Theory Formation and
Automated Mathematical Theory Exploration seem to be developing
somewhat independently without a clear differentiating
methodology. Below we discuss commonalities and differences between
the two schools of thought.

@@

We use TIP version 0.2 which contains 343 problems, each stating a single
theorem and together defining a total of 618 datatypes and 1498 functions. Most
of these are duplicates, since each problem (re-)defines all of the datatypes
and functions it involves. To avoid ambiguity we prefix the names of all
definitions with the filename it came from, and collect them into one big set.

>>>>

Equation \ref{eq:mapreduce} justifies a rewrite rule for splitting a single
$\Map$ call into multiple independent calls dealing with different sections of a
list. Such rules are useful optimisations since each call can be evaluated in
parallel, leading to the ``map/reduce'' programming paradigm.

@@

{\bf Comprehensibility} depends on the complexity of a statement. Simpler
statements are considered more interesting, hence many of the systems explore
simpler/smaller statements before complex/larger ones, to more efficiently find
those which are interesting.

@@

The latter systems all use testing to check for counterexamples, which ensures
results are empirically plausible and applicable (conditions are satisfiable,
types are inhabited, etc.). They also use a small-to-large search order,
ensuring more easily-comprehensibile conjectures are explored first.

IsaCoSy ensures novelty using a constraint system, such that no generated
expression can be simplified using a previously-found equation. The other
systems use post-hoc filters based on unification and term rewriting to discard
expressions or equations which are special-cases of some other, more general
result.

@@

Differences in background and motivation continue to be relevant
today. While the majority of work in automating mathematics has been
in symbolic manipulation and theorem proving, we are concerned here
with other aspects of mathematics, including the construction of conjectures,
(counter\nobreakdash-)examples and theorems. These tasks, along with the
formation of new definitions and concepts, are varyingly known as
``Automated Theory Formation''~\cite{lenat:77,colton:book},
``Mathematical Theory Exploration''~\cite{buchberger:06} (also sometimes
prefaced with ``Computer-Aided'', ``Automated'' or ``Algorithm-Supported''),
``Automated Mathematical Discovery''~\cite{epstein:91,colton:interestingness,esarm2008},
``Concept Formation in Discovery Systems''~\cite{haase}, and
``Automated Theorem Discovery''~\cite{roy}. Such a plethora of terminology can
be unhelpful and can mask similarities between the different fields. In
particular, the twin strands of Automated Theory Formation and
Automated Mathematical Theory Exploration seem to be developing
somewhat independently without a clear differentiating
methodology. Below we discuss commonalities and differences between
the two schools of thought.

@@

We use TIP version 0.2 which contains 343 problems, each stating a single
theorem and together defining a total of 618 datatypes and 1498 functions. Most
of these are duplicates, since each problem (re\nobreakdash-)defines all of the
datatypes and functions it involves. To avoid ambiguity we prefix the names of
all definitions with the filename it came from, and collect them into one big set.
